---
title: "Knapsack Package"
author: "Mahmood Siddique"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Knapsack Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## **What Package is Calculating**

This package has a class which consist of three methods and one constructer. constructer/initialized method is generated a dataset for the class accounding the user requirement. and then user can call any function from knapsack_brute_force, dynamic_programming or greedy_heuristich.

# **The function initialized**

constructer/initialized method is generated a dataset for the class accounding the user requirement.

# **The function brute_force_knapsack()**

This method is solving knapsack problem by using set method.

# **The function knapsack_dynamic()**

This method is solving knapsack problem by using tabular method/ dynamic programming.  

# **The function greedy_knapsack()**

This function is returning a vector of Residuals


## knapsack_brute_force

This is how function will called and output the results
```{r}
load("~/R Packages/lab6/vignettes/data.RData")
obj <- knapsack_class$new()
obj$brute_force_knapsack(obj$ks_dataset[1:8,],3500)
```
## knapsack brute force Question
  How much time does it takes to run the algorithm for n = 16 objects?
  
  Answer : it will take 2^16 = 65536  time

## knapsack_dynamic

This is how function will called and output the results

```{r}
obj <- knapsack_class$new()
obj$knapsack_dynamic(obj$ks_dataset[1:8,],3500)
```

## knapsack dynamic Question
  How much time does it takes to run the algorithm for n = 500 objects?
  Answer : it will take n X W time, if W =3500 then it will be 500 X 3500 = 1750000

## greedy_knapsack

This is how function will called and output the results
```{r}

```

## greedy knapsack Question
  How much time does it takes to run the algorithm for n = 1000000 objects?
  Answer  : it will take 6000000 time which is nlogn times
